---
title: "HW05b: Importing"
author: "Morgan Tackett"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---
##Limpets
```{r}
library(tidyverse)
limpets <- read_csv("~/BI485/tackett_morgan/data/limpets.csv")
limpets
```

```{r}
read_csv("~/BI485/tackett_morgan/data/limpets.csv", col_types = c("ncc"))
```
```{r}

sites_ordered <- limpets$Site <- factor(limpets$Site, levels = c("PBL", "KNRM", "VBG", "WP", "PF", "DP", "SIO", "CTZ1", "CTZ2", "CNM"), ordered = TRUE)
sites_ordered
```
```{r}
ggplot(data = limpets, mapping = aes(x = Site, y = Length, color = Protected)) + 
  geom_boxplot()
```
```{r}
ggplot(data = limpets, mapping = aes(x = Site, y = Length, color = Protected)) + 
  geom_boxplot() +
  labs(x = "Site", y = "Length (mm)")
```
#This boxplot shows that the three protected sites have larger limpets, WP and DP have outlyers. 

##Roseate
```{r}
roseate <- read_tsv("~/BI485/tackett_morgan/data/roseate_terns.txt")
```
```{r}
t_roseate <- roseate %>% 
  gather("AR", "AL", "AC", "BR", "BL", "BC", "JR", "JL", "JC", key = "Site", value = "Individuals")
t_roseate
```

```{r}
filter(t_roseate, is.na(Individuals) == FALSE)
```
```{r}
ggplot(data = t_roseate, mapping = aes(x = year, y = Individuals)) + 
  geom_line() +
  facet_wrap(~ Site, nrow = 2)
```
#The clearest increase in population is the AR population, other populations that seem to increase are JC, AC, AL and BC. JR dramatically decreased which is similar to BR. 

##Darter
```{r}
<<<<<<< HEAD
file_path <- "~/BI485/tackett_morgan/data"
```

```{r}
start_pos <- c(1, 4, 15, 16, 17, 18, 21, 25, 29, 33, 36, 39, 40)
stop_pos <- c(3, 14, 15, 16, 17, 20, 24, 28, 32, 35, 38, 40, 41)
names <- c("specimen id", "species", "riffle", "age", "sex", "length", "depth", "velocity", "temperature", "majsub", "minsub", "majtype", "mintype")
darters <- read_fwf(file.path(file_path, "darter.txt"), fwf_positions(start_pos, stop_pos, col_names = names), skip = 15)
```
```{r}
darters
```
```{r}
darters_riffle <- darters$riffle <- factor(darters$riffle, levels = c("1", "2"), ordered = FALSE)

```
```{r}
darters_majtype <- darters$majtype <- factor(darters$majtype, levels = c("s", "fg", "sg", "lg", "c"), ordered = TRUE)
```
```{r}
darters2 <- darters %>%
  filter(!species %in% c("zonale", "tetrazonum"))
darters2
```
```{r}
darters3 <- subset(darters2, select = -c(mintype,minsub) )
darters3
```
```{r}
colnames(darters3)[colnames(darters3)=="majsub"] <- "major_substrate"
colnames(darters3)[colnames(darters3)=="majtype"] <- "major_type"
darters3
```
```{r}
ggplot(data = darters3, mapping = aes(x = length, y = depth, color = species, shape = species)) + 
  geom_point() +
  facet_wrap(~ riffle, nrow = 2)
  
```
#Riffle one has more caeruleum with higher depth and longer spectable. 
```{r}
ggplot(data = darters3, mapping = aes(x = species, y = length)) + 
  geom_boxplot() +
  facet_wrap(~ riffle, nrow = 2)
```
#blemnioides has the most outliers.


=======
darter <- read_tsv("~/BI485/tackett_morgan/data/darter.txt")
darter
```

>>>>>>> 4e1497f781320502b015fcc58f8b006b87473623



##Abalone
```{r}
abalone <- read_csv("~/BI485/tackett_morgan/data/abalone.csv")
```

```{r}
abalone1 <- select(abalone, 2:10)
abalone1
```
```{r}
ggplot(data = abalone1, mapping = aes(x = Type, y = Height)) + 
  geom_boxplot() 
```
```{r}
ggplot(data = abalone1, mapping = aes(x = Rings, y = Height)) + 
  geom_point() 
```
#The large individuals do not correlate to old individuals. 
```{r}
abalone2 <- filter(abalone1, Height < 0.3)
abalone2
```
```{r}
abalone_type <- abalone2$Type <- factor(abalone2$Type, levels = c("I", "F", "M"), ordered = TRUE)
sites_ordered
```

```{r}
ggplot(data = abalone2, mapping = aes(x = Rings, y = Height)) + 
  geom_point() +
  facet_wrap(~ Type, nrow = 2)
```
#Female seems the largest followed by males but there is a lot in common between the three types. 

```{r}
filter(abalone2, Height == 0)
```
```{r}
abalone2[abalone2 == 0] <- NA
```
```{r}
abalone3 <- filter(abalone2, is.na(Height) == FALSE)
```
```{r}
ggplot(data = abalone3, mapping = aes(x = LongestShell, y = Diameter, color = Type)) + 
  geom_point()
```
```{r}
ggplot(data = abalone2) + 
  geom_point(mapping = aes(x = Rings, y = WholeWeight))
```

