---
title: "HW05b: Importing"
author: "Morgan Tackett"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---
##Limpets
```{r}
library(tidyverse)
limpets <- read_csv("~/BI485/tackett_morgan/data/limpets.csv")
limpets
```

```{r}
read_csv("~/BI485/tackett_morgan/data/limpets.csv", col_types = c("ncc"))
```
```{r}

sites_ordered <- limpets$Site <- factor(limpets$Site, levels = c("PBL", "KNRM", "VBG", "WP", "PF", "DP", "SIO", "CTZ1", "CTZ2", "CNM"), ordered = TRUE)
sites_ordered
```
```{r}
ggplot(data = limpets, mapping = aes(x = Site, y = Length, color = Protected)) + 
  geom_boxplot()
```
```{r}
ggplot(data = limpets, mapping = aes(x = Site, y = Length, color = Protected)) + 
  geom_boxplot() +
  labs(x = "Site", y = "Length (mm)")
```
#This boxplot shows that the three protected sites have larger limpets, WP and DP have outlyers. 

##Roseate
```{r}
roseate <- read_tsv("~/BI485/tackett_morgan/data/roseate_terns.txt")
```
```{r}
t_roseate <- roseate %>% 
  gather("AR", "AL", "AC", "BR", "BL", "BC", "JR", "JL", "JC", key = "Site", value = "Individuals")
t_roseate
```

```{r}
filter(t_roseate, is.na(Individuals) == FALSE)
```
```{r}
ggplot(data = t_roseate, mapping = aes(x = year, y = Individuals)) + 
  geom_line() +
  facet_wrap(~ Site, nrow = 2)
```
#The clearest increase in population is the AR population, other populations that seem to increase are JC, AC, AL and BC. JR dramatically decreased which is similar to BR. 

##Darter
```{r}
darter <- read_tsv("~/BI485/tackett_morgan/data/darter.txt")
darter
```




##Abalone
```{r}
abalone <- read_csv("~/BI485/tackett_morgan/data/abalone.csv")
```

```{r}
abalone1 <- select(abalone, 2:10)
abalone1
```
```{r}
ggplot(data = abalone1, mapping = aes(x = Type, y = Height)) + 
  geom_boxplot() 
```
```{r}
ggplot(data = abalone1, mapping = aes(x = Rings, y = Height)) + 
  geom_point() 
```
#The large individuals do not correlate to old individuals. 
```{r}
abalone2 <- filter(abalone1, Height < 0.3)
abalone2
```
```{r}
abalone_type <- abalone2$Type <- factor(abalone2$Type, levels = c("I", "F", "M"), ordered = TRUE)
sites_ordered
```

```{r}
ggplot(data = abalone2, mapping = aes(x = Rings, y = Height)) + 
  geom_point() +
  facet_wrap(~ Type, nrow = 2)
```
#Female seems the largest followed by males but there is a lot in common between the three types. 

```{r}
filter(abalone2, Height == 0)
```
```{r}
abalone2[abalone2 == 0] <- NA
```
```{r}
abalone3 <- filter(abalone2, is.na(Height) == FALSE)
```
```{r}
ggplot(data = abalone3, mapping = aes(x = LongestShell, y = Diameter, color = Type)) + 
  geom_point()
```
```{r}
ggplot(data = abalone2) + 
  geom_point(mapping = aes(x = Rings, y = WholeWeight))
```

