---
title: "Tackett_hw06b"
author: "Morgan Tackett"
date: "12/30/2018"
output: html_document
---
#Im happy to know you remember my ridiculous comments on my BI 153 tests lol

```{r}
library(tidyverse)
library(lubridate)
```
#Part one
```{r}
birth_date <- "02/20/1997"

# Elizabeth Garret Anderson was the first female physician
anderson <- "9 June 1836"

# Mary Anning discovered the first complete Plesiosaur fossil, 
# and other important Jurassic fossils
anning <-  "1799/05/21"

# Alice Augusta Ball was a chemist who developed the
# first injectable treatment for leprosy.
ball <- "July 24, 1892"

# Sylvia Earle was the first chieft scientist at NOAA
earle <- "August, 30 (1935)"

# Rosalind Franklin used x-ray diffraction to 
# discover DNA structure. Watson and Crick claimed credit.
franklin <- "25th of July, 1920"

# Ester Lederberg was the first to discover that viruses 
# infect bacteria. Led to discovery of lambda bacteriophage
lederberg <- "December 18, 1922"

# Barbara McClintock discovered transposable elements (jumping genes),
# and developed staining techniques to study chromosomes
mcclintock <- "16061902"

# Martin Luther King's birthday is coming up. Let's remember a dream
mlk_birth <- "1/15/29"
mlk_dream <- "1963 August 08"
```
#Question one
```{r}
morgan <- mdy(birth_date)
anderson <- dmy(anderson)
anning <- ymd(anning)
ball <- mdy(ball)
earle <- mdy(earle)
franklin <- dmy(franklin)
lederberg <- mdy(lederberg)
mcclintock <- dmy(mcclintock)
mlk_birth <- mdy(mlk_birth)
mlk_dream <- ymd(mlk_dream)
morgan
anderson
anning
ball
earle
franklin
lederberg
mcclintock
mlk_birth
mlk_dream
```
#question 2
#mlks birthday has the incorrect year. 
```{r}
mlk_birth <- update(mlk_birth, year = 1929)
mlk_birth
```
#Question three 

```{r}
morgan_day <- wday(morgan, label = TRUE, abbr = FALSE)
morgan_day
#This is correct, i was born on a thursday
```
#Question 4
```{r}
morgan2 <- update(morgan, year = 2022)
morgan2_day <- wday(morgan2, label = TRUE, abbr = FALSE)
morgan2_day
```
#Question 5
```{r}
morgan3 <- update(morgan, year = 2525)
morgan3_day <- wday(morgan3, label = TRUE, abbr = FALSE)
age = year(morgan3) - year(morgan)
age
morgan3_day
```

#Question 6
```{r}
diff_birth <- abs(anderson - ball)
diff_birth
# Time difference of 20499 days
```
#Question 7
```{r}
birth_to_dream <- abs(mlk_birth - mlk_dream)
birth_to_dream
# Time difference of 12623 days
```
#Question 8
```{r}
births <- c("1997-02-20","1836-06-09","1799-05-21","1892-07-24","1935-08-30","1920-07-25","1922-12-18","1902-06-16","1929-01-15","1963-08-08")
names(births) <- c("morgan", "anderson", "anning", "ball", "earle", "franklin", "lederberg", "mcclintock", "mlk_birth", "mlk_dream")
births
```
```{r}
years <- year(births)
LeapYears <- leap_year(years)
Leaps <- years[LeapYears]
Leaps
```
#Looks like anderson, ball and franklin all had birthday years that were leap years.

```{r}
all_births <- ymd(births)
birthday <- all_births[1]
time_difference <- morgan - all_births
names(time_difference) <- c("morgan", "anderson", "anning", "ball", "earle", "franklin", "lederberg", "mcclintock", "king")
sort(time_difference, decreasing = TRUE)
```
#In order of farthest away from my birthday to closest, it goes, anning, anderson, ball, mcclintock, franklin, lederberg, king, earle, me 


#Part two


```{r}
file_path <-"~/BI485/tackett_morgan/data"
lake <- read.csv(file.path(file_path, "lake_ice.csv"))
lake
```

```{r}
lake_ice <- filter(lake, lakecode == "DMR1")
lake_ice
```

```{r}
lake_ice <- select(lake_ice, iceon_year, iceon_month, iceon_day, iceoff_year, iceoff_month, iceoff_day)
lake_ice
```

```{r}
lakeice <- lake_ice %>% 
  select(iceon_year, iceon_month, iceon_day, iceoff_year, iceoff_month, iceoff_day) %>% 
  mutate(ice_on = make_date(iceon_year, iceon_month, iceon_day),
         ice_off = make_date(iceoff_year, iceoff_month, iceoff_day))
lakeice
```

```{r}
lakeice2 <- lakeice %>% 
  mutate(duration = as.numeric(ice_off - ice_on))
lakeice2

```

```{r}
ggplot(data = lakeice2) +
  geom_line(mapping = aes(x = iceoff_year, y = duration), na.rm = TRUE)+
    coord_cartesian(xlim = c(1850, 2013))+
                    labs(x = "Year", y = "Ice Duration (days)")

```
#Got it!
####Soil Carbon Dioxide
```{r}
soil <- read.delim(file.path(file_path, "soil_co2.txt"))
soil
```

```{r}
jan1 <- make_date(year = 2006, day = 1, month = 1)
jan1
```

```{r}
soil_co2 <- soil %>% 
  rename(Day_number = DayN..) %>% 
  rename(Day = Datecode..) %>% 
  rename(Minute = Min..) %>% 
  rename(Vegetation_sample = Veg..) %>% 
  rename(Plot = Plot..) %>% 
  rename(Group = Group..) %>% 
  rename(CO2_concentration = CorrCO2..) %>% 
  rename(Soil_type = SoilT..)
soil
```

```{r}
soil2 <- soil %>% 
  mutate(Date = january + DayN..,
         Year = year(Date),
         Month = month(Date, label = TRUE, abbr = TRUE)) %>% 
group_by(Year, Month)
soil2
```


```{r}
soil3 <- soil2 %>%
  summarise(
    mean_CO2 = mean(CorrCO2..),
    se_Co2 = sd(CorrCO2..)/sqrt(n())
  )
soil3
```

```{r}
ggplot(data = soil3) +
  geom_col(aes(x = Month, y = mean_CO2)) +
  geom_linerange(aes(x = Month, ymin = mean_CO2 - se_Co2, ymax = mean_CO2 + se_Co2)) +
  facet_wrap(~ Year, ncol = 3)
```

```{r}
ggplot(data = soil3) +
  geom_point(aes(x = Month, y = mean_CO2)) +
  geom_linerange(aes(x = Month, ymin = mean_CO2 - se_Co2, ymax = mean_CO2 + se_Co2)) +
  facet_wrap(~Year, nrow = 2)
```
#Got it!
#Mississippi River 
```{r}
file_path <-"~/BI485/tackett_morgan/data"
thebes <- read.csv(file.path(file_path, "thebes_discharge.csv"))
````
````{r}
colnames(thebes)
thebes2 <- thebes %>%
  gather ("X1988":"X2018", key = "Year", value = "discharge") %>% 
  group_by(Year, Month) %>% 
  mutate(discharge = discharge / 1000,
         Event = case_when(
           Year== "1993" ~ "Flood",
           Year == "2011" ~ "Flood",
           Year == "1988" ~ "Drought",
           Year == "2012" ~ "Drought",
           TRUE ~ "Normal"),
         average_discharge = mean(discharge), na.rm = FALSE)
thebes2
```

```{r}
years <- thebes2 %>% 
  filter(Event %in% c("Flood", "Drought"))
years
```

```{r}
plot1 <- thebes2 %>%
  ggplot() +
  geom_line(aes(x = Month, y = average_discharge, group = Year),
            color = "gray70",
            size = 0.3) +
  labs(x = NULL,
       y = "Discharge (cf/s, thousands)")
plot1
```

```{r}
thebes2 %>%
  ggplot() +
  geom_line(aes(x = Month, y = average_discharge, group = Year),
            color = "gray70") +
  labs(x = NULL,
       y = "Discharge (cf/s, thousands)") +
  geom_line(data = years, aes(x = Month, y = average_discharge, group = Year, color = Event))
```

#Got it!



