---
title: "Tackett_hw07a"
author: "Morgan Tackett"
date: "12/31/2018"
output: html_document
---
```{r}
library(tidyverse)
library(GGally)
library(devtools)
library(patchwork)
```

```{r}
file_path <- "~/BI485/tackett_morgan/data"
```
#Tab seperated
```{r}
sparrow <- read_tsv(file.path(file_path, "sparrows.txt"))
```
```{r}
sparrow
```
```{r}
View(sparrow)
```
#Adding the two extra columns
```{r}
sparrows <- sparrow %>% 
  mutate(box_group = "Sparrows",
         row_order = 1:nrow(.))
View(sparrows)
```

#Plot two
```{r}
plot_box <-
  sparrows %>%
  ggplot(aes(x = box_group, 
             y = wingcrd)) +
  geom_boxplot(width = 0.25) + 
  labs(x = NULL,
       y = "Wing Length (mm)")
plot_box
```
#Shows outliers but they are very close to the real numbers so well make a different plot to see.
```{r}
plot_cleveland <-
  sparrows %>%ggplot(aes(x = wingcrd,
                       y = row_order)) +
  geom_point() + 
  labs(x = "Wing length (mm)", 
       y = "Order of the data")
plot_cleveland
```
#Different type of graph that will be used to merge with the first graph
```{r}
plot_box + plot_cleveland
```
#Recreated figure 2@
```{r}
plot_box + plot_cleveland + coord_flip()
```
#Fixed the axis problem! There is no real difference in the outliers so the scientists can use those numbers as well. 

#Plot three
```{r}
p_culmen <- sparrows %>% 
  ggplot(aes(y = row_order)) +
  geom_point(aes(x = culmen)) +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())
p_culmen
```
```{r}
p_nalospi <- sparrows %>% 
  ggplot(aes(y = row_order)) +
  geom_point(aes(x = nalospi)) +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())
p_nalospi
```
```{r}
p_wt <- sparrows %>% 
  ggplot(aes(y = row_order)) +
  geom_point(aes(x = wt)) +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())
p_wt
```
```{r}
p_wingcrd <- sparrows %>% 
  ggplot(aes(y = row_order)) +
  geom_point(aes(x = wingcrd)) +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())
p_wingcrd
```
```{r}
p_tarsus <- sparrows %>% 
  ggplot(aes(y = row_order)) +
  geom_point(aes(x = tarsus)) +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())
p_tarsus
```
```{r}
p_head <- sparrows %>% 
  ggplot(aes(y = row_order)) +
  geom_point(aes(x = head)) +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())
p_head
```
```{r}
p_culmen + p_nalospi + p_wt + p_wingcrd + p_tarsus + p_head + plot_layout(ncol = 3)
```
#Typing the plots in order of left to right then adding a column number of 3 gives the correct final plot. 


