---
title: "HW09"
author: "Morgan Tackett"
date: "01/09/19
output: html_notebook
---
```{r}
library(tidyverse)
library(ggthemes)
```
```{r}
file_path <- "~/BI485/tackett_morgan/data"
```
```{r}
gliadin <- read_lines(file.path(file_path, "beta_gliadin.txt"))
gliadin
```
#yay genetics
```{r}
beta_gliadin <- gliadin %>% 
  str_replace_all("\\s", "\\") %>% 
  str_replace_all("\\d", "\\") 
beta_gliadin
```

```{r}
beta_gliadin <- beta_gliadin %>% 
  str_c(collapse = "")
beta_gliadin
```

```{r}
beta_gliadin <- beta_gliadin %>% 
  str_to_upper()
beta_gliadin
str_length(beta_gliadin)
```
#all cleaned up
```{r}
str_count(beta_gliadin, "[^ACGT]")
```
#23 non ATCG letters
```{r}
str_count(beta_gliadin, "ATG")
str_count(beta_gliadin, "TGA|TTA")
```
#66 and 99 like you said!
```{r}
caat_box <- "CCAAT"
tata_box <- "CTATAA"
str_count(beta_gliadin, caat_box)
str_count(beta_gliadin, tata_box)
```
#There are 4 caat boxes and one tata box. 
```{r}
caat_seq <- "CCAAT.{100,150}ATG"
str_count(beta_gliadin, caat_seq)
```
#there are 2 sequences that match this.
```{r}
tata_seq <- "CTATAA.{50,100}ATG"
str_count(beta_gliadin, tata_seq)
```
#There is one sequence that matches this
```{r}
caat_seqs_all <- str_extract_all(beta_gliadin, caat_seq, simplify = TRUE)
str_length(caat_seqs_all)
caat_seqs_all
```

```{r}
str_which(caat_seqs_all, tata_box)
promoter <- str_subset(caat_seqs_all, tata_box)
```

```{r}
promoter
```
```{r}
str_length(promoter)
```
#139 nucleotides in this promoter
#part 2
```{r}
file_path <- "~/BI485/tackett_morgan/data"
```
#Tab seperated
```{r}
ants <- read_csv(file.path(file_path, "ants.csv"))
ants
```
```{r}
ants1 <- ants %>%
  select(-c(season, seas.code, trt, plot, sample))%>%
  gather(key = species, value = abundance, matches("\\w\\.\\w", ignore.case = FALSE))
ants1
```
```{r}
ants2 <- ants1 %>% 
  mutate(
    species = str_replace(
      species,
      pattern = "(^[A-Z]*\\w{3})\\w{3,}\\.(\\w{4})\\w{2,}",
      replacement = "\\1\\2"),
    year = factor(year, levels = c("2010", "2011"), labels = c("2010", "2011"), ordered = TRUE)) %>% 
  group_by(year, species) %>% 
  summarise(total = sum(abundance, na.rm = TRUE)
  )
ants2
```
```{r}
ants2%>%
  ggplot(aes(x = reorder(species, total), y = total, group = species))+
  geom_line(color = "gray")+
  geom_point(aes(shape = year), size = 2)+
  coord_flip()+
  labs(x = NULL, y = "Total Abundance", shape = "Year")+
  theme_minimal()
```
#got it
#part 3
```{r}
library(tidyverse)
library(htmlwidgets)
```

```{r}
flowers <- read.csv(file.path(file_path, "flower_size.csv"))
flowers
```
```{r}
flower <- flowers%>%
  filter(!is.na(Flower.number))%>%
  select(species = Species, cor_length = Corolla.length..cm., throat_width = Corolla.width.throat..cm.)
flower
```
```{r}
flower_size <- flower%>%
  separate(species, into = c("genus", "species"), sep = " ", extra = "drop")
flower_size
```
```{r}
flower_size2 <- flower_size%>%
  group_by(genus, species)%>%
  summarize(mean_length = mean(cor_length), mean_width = mean(throat_width), max_length = max(cor_length), max_width = max(throat_width))
flower_size2
```

```{r}
pollinator_raw <- read_csv(file.path(file_path, "flower_pollinators.csv"))
```
```{r}
pollinators <- pollinator_raw %>%
  select(-c(Color, starts_with("Source"))) %>%
  filter(!is.na(Pollinator)) %>%
  separate(Species, into = c("genus", "species"), sep = " ", extra = "drop")
pollinators
```
```{r}
pollinators <- pollinators %>% 
    separate(Pollinator, into = "Syndrome", sep = " |, ")
pollinators
```
#This definitely took me the longest amount of time on part 3 and ughhh


```{r}
phlox <- inner_join(flower_size2, pollinators, by = c("genus", "species"))
phlox
```
```{r}
phlox%>%
  ggplot(aes(x=mean_length, y=mean_width, color=Syndrome))+
  geom_point()
```
#YES
```{r}
phlox <- phlox%>%
  mutate(
    Syndrome = str_replace(Syndrome, "bee$", "bees"),
    Syndrome = str_replace(Syndrome, "beetle$", "beetles"))
```
```{r}
phlox%>%
  ggplot(aes(x=mean_length, y=mean_width, color=Syndrome))+
  geom_point()
```
#got it.
#thanks for telling us exactly what to do on this one. 
```{r}
phlox%>%
  group_by(Syndrome)%>%
  count(Syndrome)
```
```{r}
phlox <- phlox%>%
  mutate(Syndrome = str_replace(Syndrome, "bees|beetles", "other insects"))
phlox
```

```{r}
phlox%>%
  ggplot(aes(x=mean_length, y=mean_width, color=Syndrome))+
  geom_point()
```
```{r}
phlox <- phlox%>%
  mutate(
    syndrome_group = case_when(Syndrome == "autogamous" ~ "Autogamous",
                               Syndrome == "bat" ~ "Mammal",
                               Syndrome == "hummingbird" ~ "Bird", 
                               TRUE ~ "Insect" )
  )
phlox
```

```{r}
phlox%>%
  ggplot(aes(x=mean_length, y=mean_width, color=syndrome_group))+
  geom_point()
```
#Much more teal
```{r}
phlox%>%
  ggplot()+
  geom_point(aes(x=mean_length,
                 y=mean_width,
                 color=syndrome_group))+
  scale_color_brewer(type = "qual", palette = "Dark2")
````
```{r}
ggplot(data = phlox) +
  geom_point(mapping = aes(x = mean_length, y = mean_width, color = syndrome_group)) +
  scale_color_viridis_d(option="inferno")
```
#i like this one a lot 
```{r}
phlox%>%
  ggplot()+
  geom_point(aes(x=mean_length,
                 y=mean_width,
                 color=syndrome_group))+
  scale_color_brewer(type = "seq", palette = "Greens")
```
#i dont like the green at all. 
```{r}
phlox%>%
  ggplot()+
  geom_point(aes(x=mean_length,
                 y=mean_width,
                 color=syndrome_group))+
  scale_color_viridis_d(option = "magma")
```
#i cant see the yellow very well on this. 
```{r}
phlox%>%
  ggplot()+
  geom_point(aes(x=mean_length,
                 y=mean_width,
                 color=syndrome_group))+
  scale_color_viridis_d(option = "inferno")
```
#still cant see the yellow very well
```{r}
semo_palette <- c("#C8102E", "#DBE245", "#71C5E8", "#B07C57")
phlox%>%
  ggplot()+
  geom_point(aes(x=mean_length,
                 y=mean_width,
                 shape=syndrome_group,
                 fill=syndrome_group))+
  scale_shape_manual(values = c(22:25))+
  scale_fill_manual(values = semo_palette)
```
#This one is A-Ok
#I think i added a few too many but oh well, i was liking the different colors.
#part four
```{r}
phlox %>% 
   ggplot() +
  geom_point(aes(x = max_length,
                 y = max_width,
                 shape = syndrome_group,
                 fill = syndrome_group),
             size = 3) +
  labs(shape = "Syndrome",
       fill = "Syndrome",
       x = "Max Length (cm)",
       y = "Max Width (cm)") +
  theme_bw() +
  scale_shape_manual(values = c(21:24)) +
  scale_fill_brewer(palette = "Pastel1") +
  theme(axis.text = element_text(size = 12),
        axis.title = element_text(size = 12))
```
```{r}
phlox %>% 
   ggplot() +
  geom_point(aes(x = max_length,
                 y = max_width,
                 shape = syndrome_group,
                 fill = syndrome_group),
             size = 5) +
  labs(shape = "Syndrome",
       fill = "Syndrome",
       x = "Max Length (cm)",
       y = "Max Width (cm)") +
  theme_minimal() +
  scale_shape_manual(values = c(21:24)) +
  scale_fill_brewer(palette = "Dark2") +
  theme(axis.text = element_text(size = 8 ),
        axis.title = element_text(size = 2))
```
#ugly plot 
```{r}
phlox %>% 
  ggplot() +
  geom_point(aes(x = max_length,
                 y = max_width,
                 color = syndrome_group)) +
  labs(color = "Syndrome",
       fill = "Syndrome",
       x = "Max Length (cm)",
       y = "Max Width (cm)") +
  theme_bw() +
  scale_shape_manual(values = c(20:23)) +
  scale_color_viridis_d(option="viridis")
```
```{r}
phlox%>%
  ggplot()+
  geom_point(aes(x=mean_length,
                 y=mean_width,
                 color=syndrome_group))+
  scale_color_brewer(type = "qual", palette = "Set2")
```
#Pretty

















