---
title: "Tackett_hw06b"
author: "Morgan Tackett"
date: "12/30/2018"
output: html_document
---
```{r}
library(raster)
library(tidyverse)
library(ggthemes)
library(patchwork)
library(maptools)
library(ggmap)
library(marmap)
```
#part one
#usa map
```{r}
usa <- map_data(map = "state")
usa
```
```{r}
us_missouri <- map_data(map = "state",
                        region = "missouri")
us_missouri
```
```{r}
us_other <- subset(x = usa, 
                   subset = region %in% c("alabama",
                                          "florida",
                                          "mississippi",
                                          "north carolina"))
us_other
```
```{r}
ggplot() + 
  geom_polygon(data = us_other, 
               aes(x = long, 
                   y = lat, 
                   group = group), 
               fill = "gray")
```
```{r}
 ggplot() + 
  geom_polygon(data = us_other, 
               aes(x = long, 
                   y = lat, 
                   group = group), 
               fill = "gray") +
  geom_polygon(data = us_missouri, 
               aes(x = long, y = lat, 
                   group = group), 
               fill = "black")
```
```{r}
ggplot() + 
  geom_polygon(data = us_other, 
               aes(x = long, 
                   y = lat, 
                   group = group), 
               fill = "gray") +
  geom_polygon(data = us_missouri, 
               aes(x = long, y = lat, 
                   group = group), 
               fill = "black") +
  geom_polygon(data = usa, 
               aes(x=long, 
                   y = lat, 
                   group = group), 
               fill = NA, 
               color = "black")
```
#That is so cool
```{r}
us_map <- ggplot() + 
  geom_polygon(data = us_other, 
               aes(x = long, 
                   y = lat, 
                   group = group), 
               fill = "gray") +
  geom_polygon(data = us_missouri, 
               aes(x = long, y = lat, 
                   group = group), 
               fill = "black") +
  geom_polygon(data = usa, 
               aes(x=long, 
                   y = lat, 
                   group = group), 
               fill = NA, 
               color = "black") + 
  theme_map() +
  coord_fixed(1.3)

us_map
```
```{r}
missouri <- map_data("county", "missouri")
mo_scott <- subset(missouri, subregion %in% c("scott"))

mo_map <- ggplot() + 
  geom_polygon(data = missouri, aes(x=long, y = lat, group = group), fill = NA, color = "black") + 
  geom_polygon(data = mo_scott, aes(x = long, y = lat, group = group), fill = "black") +
  theme_map() +
  coord_fixed(1.3)

mo_map
```
#that is so cool. 
```{r}
us_map + mo_map + plot_layout(ncol = 2, widths = c(1.5,1))
```
#my turn

#That is so cool
```{r}
us_map_morgan <- ggplot() + 
  geom_polygon(data = us_missouri, 
               aes(x = long, y = lat, 
                   group = group), 
               fill = "black") +
  geom_polygon(data = usa, 
               aes(x=long, 
                   y = lat, 
                   group = group), 
               fill = NA, 
               color = "black") + 
  theme_map() +
  coord_fixed(1.3)

us_map_morgan
```

```{r}
missouri <- map_data("county", "missouri")
mo_birth <- subset(missouri, subregion %in% c("lincoln"))
mo_names <- subset(missouri, subregion %in% c("cape girardeau", "taney"))
missouri_morgan <- ggplot()+
  geom_polygon(data = mo_birth,
               aes(x = long,
                   y = lat,
                   group = group),
               fill = "black")+
  geom_polygon(data = mo_names,
               aes(x = long,
                   y = lat,
                   group = group),
               fill = "gray")+
  geom_polygon(data = missouri,
               aes(x = long,
                   y = lat,
                   group = group),
               fill = NA,
               color = "black")+
  theme_map()+
  coord_fixed(1.3)

```
```{r}
us_map_morgan + mct_counties + plot_layout(ncol = 2, widths = c(1.5,1))
```

#I was born in missouri. I really dont know what county i was born in but i grew up in lincoln county so i choose that to be my fake birth spot. Im lucky to have Colleen as my middle name because i got to use cape county. and ive never been to taney county but it stated with a T so yeah. 
#part two

```{r}
min_long <- -126
max_long <- -104
min_lat  <-   31
max_lat  <-   50

set.seed(9618973)
```

```{r}
bigfoot <- read_csv("data/bigfoot.csv")

bigfoot <- filter(bigfoot,
                  long >= min_long & long <= max_long,
                  lat >= min_lat & lat <= max_lat) %>% 
  sample_n(300) %>% 
  mutate(name = "Gigantopithecus") %>% 
  select(name, long, lat)
bigfoot
```
```{r}
bears <- read_csv("data/bears.csv")

both_species <- bind_rows(bigfoot, bears)

head(both_species)
```
```{r}
tail(both_species)
```
```{r}
base = get_stamenmap(bbox = c(min_long, 
                              min_lat, 
                              max_long, 
                              max_lat),
                     zoom = 4, 
                     maptype = "terrain-background")

ggmap(base)
```
#wow
```{r}
base <- ggmap(base)

base + geom_point(data = bigfoot,
                  aes(x = long,
                      y = lat))
```
#Lots of seatle, i dont blame bigfoot though, seatle seems like a great place 
```{r}
base + geom_point(data = bears,
                  aes(x = long,
                      y = lat))

```
#black bears dont have the same sightings as bigfoot but somewhat similar
#lets really find out
```{r}
base + geom_point(data = both_species,
                  aes(x = long,
                      y = lat,
                      shape = name,
                      fill = name),
                  size = 2) +
  scale_shape_manual(values = c(22:23)) +
  labs(x = "Longitude",
       y = "Latitude",
       fill = "Species",
       shape = "Species")
```
#okay, so maybe bigfoot is a bear...
#my turn
```{r}
min_long <- -126
max_long <- -104
min_lat  <-   31
max_lat  <-   50

set.seed(1933056)
```

```{r}
bigfootso <- read_csv("data/bigfoot.csv")

bigfootso <- filter(bigfootso,
                  long >= min_long & long <= max_long,
                  lat >= min_lat & lat <= max_lat) %>% 
  sample_n(300) %>% 
  mutate(name = "Gigantopithecus") %>% 
  select(name, long, lat)
bigfoot
```

```{r}
bears <- read_csv("data/bears.csv")

both_species <- bind_rows(bigfootso, bears)

head(both_species)
```
```{r}
tail(both_species)
```
```{r}
base = get_stamenmap(bbox = c(min_long, 
                              min_lat, 
                              max_long, 
                              max_lat),
                     zoom = 4, 
                     maptype = "terrain-background")

ggmap(base)
```
```{r}
base <- ggmap(base)

base + geom_point(data = bigfootso,
                  aes(x = long,
                      y = lat))
```
#my SO realllly likes seatle, even more than last time
88
```{r}
base + geom_point(data = bears,
                  aes(x = long,
                      y = lat))

```
```{r}
base + geom_point(data = both_species,
                  aes(x = long,
                      y = lat,
                      shape = name,
                      fill = name),
                  size = 2) +
  scale_shape_manual(values = c(22:23)) +
  labs(x = "Longitude",
       y = "Latitude",
       fill = "Species",
       shape = "Species")
```
#This looks very similar to the one above but it is not the same. I redid every step so i wouldnt miss anything.
#part three
```{r}
min_long <- -170
max_long <- 164
min_lat  <- -42
max_lat  <- -8
earthquakes <- quakes %>% 
   mutate(depth = depth * 3280.84)
```
```{r}

fiji <- getNOAA.bathy(lon1 = min_long,
                      lon2 = max_long,
                      lat1 = min_lat,
                      lat2 = max_lat,
                      antimeridian = TRUE,
                      keep = TRUE)
```

```{r}
autoplot.bathy(fiji, 
         geom = c("raster", "contour"),
         size = 0.05,
         na.rm = TRUE)
```
#went back and changed .1 to .05 for not much of a difference but a little. kept as .05 on this step but then changed back to .1 to keep the same as you.
```{r}
autoplot(fiji, 
         geom = c("raster","contour"),
         size = 0.1,
         na.rm = TRUE) +
  scale_fill_gradient2(low = "dodgerblue4", 
                       mid = "gainsboro", 
                       high = "darkgreen",
                       name = "Depth (ft)") +
  labs(x = "Longitude",
       y = "Latitude") +
  theme(axis.title.y = element_text(angle = 0, 
                                    vjust = 0.5))
```
#my last two pictures are much darker than yours, im not sure what i did wrong, it looks exactly the same as yours.
```{r}
base_map <- autoplot(fiji, 
                     geom = c("raster","contour"),
                     size = 0.1,
                     na.rm = TRUE) +
  scale_fill_gradient2(low = "dodgerblue4", 
                       mid = "gainsboro", 
                       high = "darkgreen",
                       name = "Depth (ft)") +
  labs(x = "Longitude",
       y = "Latitude") +
  theme(axis.title.y = element_text(angle = 0, 
                                    vjust = 0.5))
```
```{r}
base_map + 
  geom_point(data = earthquakes,
             aes(x = long,
                 y = lat))
```
#very high contrast, not like yours but the code is the exact same. 
```{r}
base_map + 
  geom_point(data = earthquakes,
             aes(x = long,
                 y = lat,
                 size = mag),
             alpha = 0.4)
```

```{r}
base_map + 
  geom_point(data = earthquakes,
             aes(x = long,
                 y = lat,
                 size = mag),
             alpha = 0.4) +
  scale_size_continuous(range = c(0.5,3), name = "Magnitude")
```

#my turn
```{r}
min_long <- -90
max_long <- -58
min_lat <- 8
max_lat <- 28
```
```{r}
file_path <-"~/BI485/tackett_morgan/data"
blennies <- read.csv(file.path(file_path, "blennies.csv"))
blennies
```
```{r}
carib_sea <- getNOAA.bathy(lon1 = min_long,
                           lon2 = max_long,
                           lat1 = min_lat,
                           lat2 = max_lat,
                           antimeridian = FALSE,
                           keep = TRUE)
```
```{r}
base_map <- autoplot(carib_sea,
         geom = c("raster", "contour"),
         size = 0.1,
         na.rm = TRUE) +
  scale_fill_etopo(guide = FALSE)+
  labs(x = "Longitude",
       y = "Latitude")+
  theme(axis.title.y = element_text(angle = 0,
                                    vjust = 0.5))
base_map
```

```{r}
base_map + geom_point(data = blennies,
                      aes(x = long,
                          y = lat,
                          shape = name),
                      fill = "white",
                      size =2.5)+
  scale_shape_manual(values = c(21:23))+
  labs(shape = "Species")+
  theme(legend.position = "bottom")+
  theme(legend.text = element_text(face = "italic"))

```
#Got it. This was by far the most fun homework assignment. 
