---
title: "Tackett_hw06b"
author: "Morgan Tackett"
date: "12/30/2018"
output: html_document
---
```{r}
library(tidyverse)
library(knitr)
library(smatr)
```
```{r}
file_path <- "~/BI485/tackett_morgan/data"
```
#plot 1
```{r}
darters <- read.delim(file.path(file_path, "darter.txt"))
Column_start <- c(1, 4, 15, 16, 17, 18, 21, 25, 29, 33, 36, 39, 40)
Column_stop <- c(3, 14, 15, 16, 17, 20, 24, 28, 32, 35, 38, 40, 41)
names <- c("specimen id", "species", "riffle", "age", "sex", "length", "depth", "velocity", "temperature", "majsub", "minsub", "majtype", "mintype")
darter_t <- read_fwf(file.path(file_path, "darter.txt"), fwf_positions(Column_start, Column_stop, col_names = names), skip = 15)
darter_t2 <- darter_t %>%
  filter(!species %in% c("zonale", "tetrazonum"))
```
```{r}
darter_t2
```
```{r}
mutate(darter_t2, total_substrate = majsub + minsub)
```
#Total substrate = 1
```{r}
darter_t2$riffle[darter_t2$riffle==1] <- "Riffle_1"
darter_t2$riffle[darter_t2$riffle==2] <- "Riffle_2"
darter_t2$sex[darter_t2$sex=="f"] <- "Female"
darter_t2$sex[darter_t2$sex=="m"] <- "Male"
darter_t2 <- mutate(darter_t2, length = length * 10)
darter_t2
```
```{r}
darter_means <- darter_t2 %>% group_by(species) %>%
  summarise_at(.vars = vars(length, depth, velocity), 
               .funs = c(mean = "mean")) 
darter_means
```
```{r}
ggplot(data = darter_t2) +
  stat_summary(
    mapping = aes(x = species, y = length),
    fun.ymin = min,
    fun.ymax = max,
    fun.y = median
  ) +
  geom_point(data = darter_means, mapping = aes(x = species, y = length_mean), shape = 15) + 
  coord_flip() +
    facet_wrap(~ riffle) +
   ylab("Length (mm)") + xlab("Species")
```
#Riffle one seems to have much larger values than riffle two.
#plot 2
```{r}
ggplot(data = darter_t2, mapping = aes(x=length, y=species))+
  geom_point(color = "grey55")
```
```{r}
ggplot(data=darter_t2, mapping = aes(x=length, y=species))+
  stat_summary(mapping = aes(x=length, y=species),
               fun.y = median,
               geom = "point",
               size = 2.2
               )+
  geom_point(color="grey55")
```

```{r}
ggplot(data = darter_t2, mapping = aes(x=length, y=species))+
  stat_summary(mapping = aes(x=length, y=species),
               fun.y = median,
               geom = "point",
               size=2.2
               )+
  geom_point(color="grey55")+
  stat_summary(mapping = aes(x=length, y=species),
               fun.y = mean,
               geom = "point",
               size=3,
               color = "maroon"
               )
```

```{r}
ggplot(data = darter_t2
       , mapping = aes(x=length, y=species))+
  stat_summary(mapping = aes(x=length, y=species),
               fun.y = median,
               geom = "point",
               size=2.2
               )+
  geom_point(color="grey55")+
  stat_summary(mapping = aes(x=length, y=species),
               fun.y = mean,
               geom = "point",
               size=3,
               color = "maroon"
               )+
  coord_flip()+
  facet_wrap(~ riffle, nrow=2)+
  labs(y=NULL, x="Length (cm)")
```
#I do not see a clear pattern to this data, however riffle oe has less breaks in length than riffle two. 

##Stress and corticosterones in birds
```{r}
names <- c("capture_date", "day", "site", "urban_score", "cortF", "cortB", "sex", "smi", "tarsus", "mass", "basal_cort", "stress_cort")
feathers <- read_csv(file.path(file_path, "feathers.csv"), locale = locale(decimal_mark = ","), skip = 1, col_names = names)
feathers
```
#Already tidy
```{r}
mean_tarsus <- mean(feathers[["tarsus"]])
mean_tarsus
```
```{r}
feathers2 <- mutate(feathers, log_mass = log(mass), log_tarsus = log(tarsus))
feathers2
```
```{r}
major_axis <- sma(log_mass ~ log_tarsus, data = feathers2)
summary(major_axis)
```
```{r}
coef(major_axis)
b <- 1.864889
```
```{r}
feathers3 <- mutate(feathers2, new_smi = mass * (mean_tarsus / tarsus) ^ b)
feathers3
```
```{r}
feathers3 %>%
  group_by(site)
```
```{r}
mean_basal_cort <- mean(feathers3$basal_cort, na.rm = TRUE)
mean_stress_cort <- mean(feathers3$stress_cort, na.rm = TRUE)
sd_basal_cort <- sd(feathers3$basal_cort, na.rm = TRUE)
sd_stress_cort <- sd(feathers3$stress_cort, na.rm = TRUE)
se_basal_cort <- sd_basal_cort/(sqrt(43))
se_stress_cort <- sd_stress_cort/(sqrt(43))
```
```{r}
ggplot(data = feathers3, mapping = aes(x = new_smi, y = site)) + 
  geom_boxplot()
```
#Villefollet has new_smi between 24-25, nort has new_smi between 22 and 23. larochelle has new_smi between 23 and 24 and cebc has new_smi above 25
```{r}
min_basal <- mean_basal_cort - se_basal_cort
max_basal <- mean_basal_cort + se_basal_cort
ggplot(data = feathers3, mapping = aes(x = site, y = basal_cort)) + 
  geom_point() +
  geom_errorbar(ymin = min_basal, ymax = max_basal)
```
```{r}
min_stress <- mean_stress_cort - se_stress_cort
max_stress <- mean_stress_cort + se_stress_cort
ggplot(data = feathers3, mapping = aes(x = site, y = stress_cort)) + 
  geom_point() +
  geom_linerange(ymin = min_stress, ymax = max_stress)
```

##Honors contract
#Modifying stress plot 3
```{r}
min_stress <- mean_stress_cort - se_stress_cort
max_stress <- mean_stress_cort + se_stress_cort
ggplot(data = feathers3, mapping = aes(x = site, y = stress_cort)) + 
  geom_point() +
  geom_linerange(ymin = min_stress, ymax = max_stress)
geom_point(data = stress_cort),
             aes(x = site,
                 y = stress_cort),
             color = "maroon",
             size = 3)
```
