---
title: "HW 06 Part 1: Complete the sections"
author: "Morgan Tackett"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---
```{r}
library(tidyverse)
```
```{r}
library(nycflights13)
flights
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

- Change "your name" in the YAML header above to your name.

- As usual, enter the examples in code chunks and run them, unless told otherwise.

## Chapter 5: Data transformation

Read [R4ds Chapter 5: Data transformation](https://r4ds.had.co.nz/transform.html), sections 5-7.

### Section 5.5: Add new variables with `mutate()`




```{r}
library(tidyverse)
library(nycflights13)
```

This creates the columns gain and speed and puts it with the previous data
```{r}
flights_sml <- select(flights, 
  year:day, 
  ends_with("delay"), 
  distance, 
  air_time
)
mutate(flights_sml,
  gain = dep_delay - arr_delay,
  speed = distance / air_time * 60
)
```

This uses gain and hours to work "mutate()" and creates "gain_per_hour".
```{r}
mutate(flights_sml,
  gain = dep_delay - arr_delay,
  hours = air_time / 60,
  gain_per_hour = gain / hours
)
```

This makes a chart only seeing the columns gain, hours, and gain_per_hour.
```{r}
transmute(flights,
  gain = dep_delay - arr_delay,
  hours = air_time / 60,
  gain_per_hour = gain / hours
)
```

This makes a collum for hour and minutes from the dep_time
```{r}
transmute(flights,
  dep_time,
  hour = dep_time %/% 100,
  minute = dep_time %% 100
)
```

This code makes a list of leading and lagging values using "lag(x)" and "lead(x)".
```{r}
(x <- 1:10)
lag(x)
lead(x)
```

This finds the sum and  mean of "x".
```{r}
x
cumsum(x)
cummean(x)
```

This uses "min_rank()" to rank data from "y" in a increasing order and "min_rank(desc())" to rank in descending order
```{r}
y <- c(1, 2, 2, NA, 3, 4)
min_rank(y)
min_rank(desc(y))
```

This uses "row_number()", "dense_rank()", "percent_rank()", and "cume_dist()" as  ways to rank data in increasing order.
```{r}
row_number(y)
dense_rank(y)
percent_rank(y)
cume_dist(y)
```

### Section 5.6: Grouped summaries with `summarise()`

This uses sumarise to only show delays
```{r}
summarise(flights, delay = mean(dep_delay, na.rm = TRUE))
```

This picks out the important data that will be used and then makes the average delay time
```{r}
by_day <- group_by(flights, year, month, day)
summarise(by_day, delay = mean(dep_delay, na.rm = TRUE))
```

This groups data by desitination, Find the mean data, filters and plots the data
```{r}
by_dest <- group_by(flights, dest)
delay <- summarise(by_dest,
  count = n(),
  dist = mean(distance, na.rm = TRUE),
  delay = mean(arr_delay, na.rm = TRUE)
)
delay <- filter(delay, count > 20, dest != "HNL")
ggplot(data = delay, mapping = aes(x = dist, y = delay)) +
  geom_point(aes(size = count), alpha = 1/3) +
  geom_smooth(se = FALSE)
```

This does the exact same thing as the plot above
```{r}
delays <- flights %>% 
  group_by(dest) %>% 
  summarise(
    count = n(),
    dist = mean(distance, na.rm = TRUE),
    delay = mean(arr_delay, na.rm = TRUE)
  ) %>% 
  filter(count > 20, dest != "HNL")
```

This shows you what happens if you miss part of the code, it gives a lot of missing data
```{r}
flights %>% 
  group_by(year, month, day) %>% 
  summarise(mean = mean(dep_delay))
```

This fixes the previous mistake by using "na.rm = TRUE"
```{r}
flights %>% 
  group_by(year, month, day) %>% 
  summarise(mean = mean(dep_delay, na.rm = TRUE))
```

This makes a data set that contains no missing flights
```{r}
not_cancelled <- flights %>% 
  filter(!is.na(dep_delay), !is.na(arr_delay))
not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(mean = mean(dep_delay))
```

This finds the average delay and then plots that
```{r}
delays <- not_cancelled %>% 
  group_by(tailnum) %>% 
  summarise(
    delay = mean(arr_delay)
  )
ggplot(data = delays, mapping = aes(x = delay)) + 
  geom_freqpoly(binwidth = 10)
```

THis makes the plot of average delay and flights
```{r}
delays <- not_cancelled %>% 
  group_by(tailnum) %>% 
  summarise(
    delay = mean(arr_delay, na.rm = TRUE),
    n = n()
  )
ggplot(data = delays, mapping = aes(x = n, y = delay)) + 
  geom_point(alpha = 1/10)
```

This makes the plot a little easier to read by getting rid of unnessicary data
```{r}
delays %>% 
  filter(n > 25) %>% 
  ggplot(mapping = aes(x = n, y = delay)) + 
    geom_point(alpha = 1/10)
```

This calculates average arr_delay
```{r}
not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(
    avg_delay1 = mean(arr_delay),
    avg_delay2 = mean(arr_delay[arr_delay > 0])
  )
```

This calculates the standard deviation of distance, then orders it in decreasing order
```{r}
not_cancelled %>% 
  group_by(dest) %>% 
  summarise(distance_sd = sd(distance)) %>% 
  arrange(desc(distance_sd))
```

This calculates the minimum and maximum not canclled. then lists min as first and max as last 
```{r}
not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(
    first = min(dep_time),
    last = max(dep_time)
  )
```

This finds the first and last departure time per day
```{r}
not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(
    first_dep = first(dep_time), 
    last_dep = last(dep_time)
  )
```

This find new variable R
```{r}
not_cancelled %>% 
  group_by(year, month, day) %>% 
  mutate(r = min_rank(desc(dep_time))) %>% 
  filter(r %in% range(r))
```

This makes carrier, then orders them in decreasing order
```{r}
not_cancelled %>% 
  group_by(dest) %>% 
  summarise(carriers = n_distinct(carrier)) %>% 
  arrange(desc(carriers))
```

This gives a count of "dest".
```{r}
not_cancelled %>% 
  count(dest)
```

This shows the miles the plane flew
```{r}
not_cancelled %>% 
  count(tailnum, wt = distance)
```

This makes the variables named "n_early" and "hour_perc".
```{r}
not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(n_early = sum(dep_time < 500))
not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(hour_perc = mean(arr_delay > 60))
```

This focuses in on one category more effectively
```{r}
daily <- group_by(flights, year, month, day)
(per_day   <- summarise(daily, flights = n()))
(per_month <- summarise(per_day, flights = sum(flights)))
(per_year  <- summarise(per_month, flights = sum(flights)))
```

This ungroups the data
```{r}
daily %>% 
  ungroup() %>%       
  summarise(flights = n())
```


### Section 5.7: Grouped mutates (and filters)
This finds the least popular of each category
```{r}
flights_sml %>% 
  group_by(year, month, day) %>%
  filter(rank(desc(arr_delay)) < 10)
```

This finds popular destinations
```{r}
popular_dests <- flights %>% 
  group_by(dest) %>% 
  filter(n() > 365)
popular_dests
```

This creates"prop_delay" 
```{r}
popular_dests %>% 
  filter(arr_delay > 0) %>% 
  mutate(prop_delay = arr_delay / sum(arr_delay)) %>% 
  select(year:day, dest, arr_delay, prop_delay)
```

